Stay in shape! Homework exam II

### 2016-03-31 geometricAlgorithms/homeworkExam/2/homeworkExam.tex
most of the psuedo code foundation for calulate the biggest disk

\begin{algorithmic}[1]
	\Function{calulateBiggestDisk}{$H$}
		\State
		$d_0 \gets arbitrarlyLargeDisk()$
		\If{hasArbitrarlylargeDisc($H$)}
			\State
			\Return $d_0$
		\EndIf
		\State
		$H_r \gets$ random shuffle $H$
		\For{$i\gets 1$ to $n$ with $h_i \in H_r$}
			\State
			$d_i \gets d_{i-1}$
			\If{$d_{i-1} \not\subset h_i$}
			\State
			$d_i \gets createLargestDiskFrom(h_i, \{h_0\dots,h_{i-1}\})$
			\EndIf
		\EndFor
	\EndFunction
\end{algorithmic}

>>>>

\begin{algorithmic}[1]
	\Function{calulateBiggestDisk}{$H$}
		\State
		$d_0 \gets arbitrarlyLargeDisk()$
		\If{hasArbitrarlylargeDisc($H$)}
			\State
			\Return $d_0$
		\EndIf
		\State
		$H_r \gets$ random shuffle $H$
		\For{$i\gets 1$ to $n$ with $h_i \in H_r$}
			\State
			$d_i \gets d_{i-1}$
			\If{$d_{i-1} \not\subset h_i$}
			\State
			$d_i \gets calculateBiggestDisk(h_i, \{h_0\dots,h_{i-1}\})$
			\EndIf
		\EndFor
	\EndFunction
	\Function{calulateBiggestDisk}{$h_{bound}$,$H_{prev}$}
		\State
		$d_0 \gets arbitrarlyLargeDisk()$
		\For{$i\gets 1$ to $n$ with $h_i \in H_{prev}$}
			\State
			$d_i \gets d_{i-1}$
			\If{$h_i$ does not point in the same direction as $h_{bound}$}
			\If{$d_{i-1} \not\subset h_i$}
				\If{$h_i \cap h_{bound}$ does not intersect the x-axis}
					\State
					\Return $None$
				\EndIf
				\If{$h_i$ is parralel to the x axis}
					%TODO: parralel to x axis!
					$d_i \gets$ Calulate the largest disk by
					creating an imaginary triangle with vertex $a$ being the
					intersection between $l_i$ and $l_{bound}$ and vertex $b$
				\Else
					$d_i \gets$ Calulate the largest disk by
					creating an imaginary triangle with vertex $a$ being the
					intersection between $l_i$ and $l_{bound}$ and vertex $b$
					and $c$ being the $-Ycoordinate(a)$ equal to $l_i$ and
					$l_{bound}$ respectivily. (because you use negative Y
					coordinate the disk center will always be on the x axis).
				\EndIf
				\State
			\EndIf
			\EndIf
		\EndFor

	\EndFunction
\end{algorithmic}
